Hydra Battles and Cie

### 2021-07-23 doc/chapter-primrec.tex
more snippets

\begin{Coqsrc}
Fact compose_01 :
    forall (x:PrimRec 0) (t : PrimRec 1),
    let c := evalPrimRec 0 x in
    let f := evalPrimRec 1 t in
    evalPrimRec 0 (composeFunc 0 1
                               (PRcons 0 0 x (PRnil 0))
                               t)  =
     f c.
Proof. reflexivity. Qed.
\end{Coqsrc}

Thus, we get a quite simple proof of \texttt{const1\_NIsPR}.

\vspace{4pt}
\noindent
\emph{From \href{../theories/html/hydras.MoreAck.PrimRecExamples.html}{MoreAck.PrimRecExamples}}.
\begin{Coqsrc}
Lemma  const1_NIsPR n : isPR 0 n. 
Proof.
  induction n.
  - apply zeroIsPR.
  - destruct IHn as [x Hx].
   exists (composeFunc 0 1 (PRcons 0 0 x (PRnil 0)) succFunc). 
   cbn in *; intros; now rewrite Hx.
Qed.
\end{Coqsrc}

@@

We prove that the library function \texttt{plus} is extensionally equal to a function defined with
\texttt{nat\_rec}.

\begin{Coqsrc}
Definition plus_alt x y  :=
              nat_rec  (fun n : nat => nat)
                       y
                       (fun z t =>  S t)
                       x.

Lemma plus_alt_ok:
  extEqual 2 plus_alt plus.
Proof.
  intro x; induction x; cbn; auto.
  intros y; cbn; now rewrite <- (IHx y).
Qed.
\end{Coqsrc}

A last lemma before the proof:

\begin{Coqsrc}
Lemma isPR_extEqual_trans n : forall f g, isPR n f ->
                                    extEqual n f g ->
                                    isPR n g.
Proof.
 intros f g [x Hx]; exists x.
 apply extEqualTrans with f; auto.
Qed.
\end{Coqsrc}

Let us start now.

@@

\begin{Coqanswer}
filter010IsPR :
forall g : nat -> nat, isPR 1 g -> isPR 3 (fun _ b _ : nat => g b)
\end{Coqanswer}

@@

\begin{Coqsrc}
 - unfold plus_alt; apply ind1ParamIsPR.
    + apply filter010IsPR, succIsPR.
    + apply idIsPR.
  - apply plus_alt_ok. 
Qed.
\end{Coqsrc}

@@

The following proof decomposes the \texttt{double} function as the composition of 
multiplication with the identity and the constant function which returns $2$.
\emph{Note that the lemma \texttt{const1\_NIsPR} considers this function as an unary function (unlike \texttt{const0\_NIsPR})}.

\begin{Coqsrc}
Lemma doubleIsPR : isPR 1 double.
Proof.
  unfold double; apply compose1_2IsPR.
  - apply idIsPR.
\end{Coqsrc}

\begin{Coqanswer}
subgoal 1 (ID 110) is:
 isPR 1 (fun _ : nat => 2)
subgoal 2 (ID 111) is:
 isPR 2 Init.Nat.mul
\end{Coqanswer}

 \begin{Coqsrc}
  - apply const1_NIsPR.
  - apply multIsPR.
Qed.
\end{Coqsrc}

>>>>

\vspace{4pt}
\input{movies/snippets/PrimRecExamples/compose01}

\vspace{4pt}
Thus, we get a quite simple proof of \texttt{const1\_NIsPR}.

\input{movies/snippets/PrimRecExamples/const0NIsPR}

@@

The following lemma shows it suffices to prove that
Standard library's function \texttt{plus} is extensionally equal to a function defined with
\texttt{nat\_rec}.

\input{movies/snippets/PrimRecExamples/isPRExtEqualTrans}

Thus, let us define an helper and prove its equivalence with \texttt{plus}.

\input{movies/snippets/PrimRecExamples/plusAlt}

We are now able to complete the proof.

\input{movies/snippets/PrimRecExamples/plusIsPRa}

@@

\vspace{4pt}
\input{movies/snippets/PrimRecExamples/checkFilter0101IsPR}
\vspace{4pt}

@@

\input{movies/snippets/PrimRecExamples/plusIsPRb}

@@

The following proof decomposes the \texttt{double} function as the composition of 
multiplication with the identity and the constant function which returns $2$.
\emph{Note that the lemma \texttt{const1\_NIsPR} considers this function as an unary function (unlike \texttt{const0\_NIsPR})}. 
\input{movies/snippets/PrimRecExamples/doubleIsPRa}
\input{movies/snippets/PrimRecExamples/doubleIsPRb}
